A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-11-09 paper/paper.tex
add nice sphere pictures Tested everything.
recompute some of the sphere data Tested everything.
new sphere data Tested everything.

>>>>

\section{Hard sphere solute}

Figure~\ref{fig:sphere-energy-vs-diameter} shows the hydration free
energy per unit surface area of a hard sphere.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/sphere-energy-vs-diameter}
\end{center}
\caption{ Free energy versus radius for a single hydrophobic sphere
immersed in water. This should have an asymptote equal to the surface
tension at room temperature, and it agrees well with the surface tension in
Figure~\ref{fig:surface-tension}. }
\label{fig:sphere-energy-vs-diameter}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/sphere-density}
\end{center}
\caption{ Density profiles illustrating the transition from vapor 
to liquid water between the rods. The radius is 0.5~nm, the top figure is 
at a separation of 0.2~nm and the
bottom is 0.6~nm. Figures~\ref{fig:rods-energy-vs-distance}~and~\ref{fig:energy-rods} show
the energy for these and other separations.}
\label{fig:sphere-density}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{figs/density-sphere}
\end{center}
\caption{ Density profiles for spheres of different radii. The dotted line
represents the saturated liquid density.  }
\label{fig:density-sphere}
\end{figure}
